PAMELA: an annotation-based Java Modeling Framework

### 2021-04-23 implementation.tex
Updates from Overleaf

Compared to a basic POJO implementation, the use of PAMELA implies a CPU and memory-footprint overhead. This is  due to the partially-interpreted nature of some of its features. We have developed a performance workbench in order to measure it \footnote {\url{https://github.com/openflexo-team/pamela/tree/1.6.1/pamela-perf-tests}}.

@@

Note however that the measured overhead only applies to a very small portion of the code (mostly property accessors methods).  A "real-world" model implementation generally involves a bigger "business code" part, which is generally the first CPU-time consumer. Using PAMELA won’t increase CPU use on "business code" if this code is implemented with plain Java code (which is generally the case). We have used the Yourkit Java Profiler\footnote{https://www.yourkit.com/} on PAMELA based applications and, as expected, the time passed on accessors was negligible compared to the time used on methods implementing business logic. As we will see in the next section, PAMELA has been successfully applied to many industrial projects, with no performance issues reported. Moreover, the PAMELA implementation offers many functional features which are not present in the base implementation (such as undo/redo, clipboard management, runtime monitoring and weaving, etc.) which out-weight the performance overhead.

>>>>

Compared to a basic POJO implementation, the use of PAMELA implies a CPU and memory footprint overhead. This is  due to the partially interpreted nature of some of its features. We have developed a performance workbench in order to measure it \footnote {\url{https://github.com/openflexo-team/pamela/tree/1.6.1/pamela-perf-tests}}.

@@

Note, however that the measured overhead only applies to a very small portion of the code (mostly property accessors methods).  A "real-world" model implementation generally involves a bigger "business code" part, which is generally the first CPU-time consumer. Using PAMELA won’t increase CPU use on "business code" if this code is implemented with plain Java code (which is generally the case). We have used the Yourkit Java Profiler\footnote{https://www.yourkit.com/} on PAMELA based applications and, as expected, the time passed on accessors was negligible compared to the time used on methods implementing business logic. As we will see in the next section, PAMELA has been successfully applied to many industrial projects, with no performance issues reported. Moreover, the PAMELA implementation offers many functional features which are not present in the base implementation (such as undo/redo, clipboard management, runtime monitoring and weaving, etc.) which outweigh the performance overhead.
